### 2016-07-25 draft.tex
modifying section 2.

	\section{Introduction}
	\section{Math details}
	The process is similar in many ways to restrictions on axion emission from supernova cooling. The procedure therefore roughly follows the analogous calculation for axions, as laid out by Raffelt. 
	\subsection{Bremsstrahlung amplitude calculation}
	 There are two processes to consider: the pp bremsstrahlung $ p+p \rightarrow p+p+A$ and the pn $ p+n \rightarrow p+n+A\ $. For the pp case, there are eight tree-level diagrams, as shown in Fig. ; for the pn, five diagrams, as shown in Fig. . \newline

>>>>

	\section{Introduction}
	\section{Computational details}
	The process we are considering, the bremsstrahlung of a dark photon from nucleon-nucleon scattering, is similar in many ways to the classic calculation of axion emission from supernova cooling. The differences arise due to the mass of the dark photon, which can be on the order of the temperature of the supernova.  This leads to different kinematics compared to the axion case.  However, the calculation roughly follows the analogous calculation for axions, as laid out by Raffelt, which we briefly review below. 
	\subsection{Bremsstrahlung amplitude calculation}
	 There are two processes to consider: the pp bremsstrahlung $ p+p \rightarrow p+p+A$ and the pn $ p+n \rightarrow p+n+A\ $. For the pp case, there are eight tree-level diagrams, as shown in Fig. ; for the pn, five diagrams, as shown in Fig. . \newline
